Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-05-11 WSSSPE4_report/WSSSPE4_report.tex
fixing a typo and some formatting - will update in arXiv later

The following four papers belong to the first area: the academic environment.
They address diverse aspects ranging from incentives for quality software to
dvocating a professional society for research software to roles and degrees for
research software engineers. For talks with multiple authors, an
\textsuperscript{\textasteriskcentered} indicates the author who presented the talk.

@@

>>>>

The following four papers belong to the first area: the academic environment.
They address diverse aspects ranging from incentives for quality software to
advocating a professional society for research software to roles and degrees for
research software engineers. For talks with multiple authors, an
\textsuperscript{\textasteriskcentered} indicates the author who presented the talk.

@@

\begin{itemize}
